\normalfont\spacedallcaps{The economic consequences of different attitudes of a policy maker: a combined epidemiological-econometric study}

### 2021-03-23 Manuscript/manuscript.tex
PUb

As a consequence, the lock-down efficacy,  within certain limits,  can be tuned.  In the literature, different scholars \cite{kabir2020evolutionary,rowthorn2020cost} challenged the issue of finding the optimal lock-down policy for minimizing the economic impact as well as the deaths.  In particular, for the model in Ref. \cite{kabir2020evolutionary} it is assumed that the policy-maker perfectly knows the consequences of his/her choices and that he/she can act without delay to impose the optimal choice; finally, it is assumed that the PM can impose a continuous factor for the lock-down (e.g., he/she can reduce the daily number of contacts between people by choosing each value between a definite range). In contrast, for different countries, such a factor seems to be much more discrete (e.g., the PM can reduce the daily contacts only by choosing definite values).  It can be argued that most of these drawbacks of this last formidable research are entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy-maker.  On this basis, we would propose here an alternative way to model the decision of the policy-maker that is based on a stochastic model instead of on a deterministic one.  Furthermore,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on redundancy funds (\textit{Cassa Integrazione Ordinaria}) in Italy.  Thus, the final output of the model will be the cumulative deaths, the economic damage for each sales sector and the the increase of redundancy funds paid.
Moreover, here we also considered that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them may be recovered or even should take the intensive therapy.  As we will show by varying with continuity the probabilistic parameter by which the PM imposes the lock-down,  a discontinuity in the SIRD model and the lock-down days was obtained.  Such behaviour belongs to a class of phenomena that, in physical sciences, is called a phase transition.  For each phase, we will discuss the result of the simulation, and then we will compare them to get a general insight.

@@

\begin{table}[]
\begin{center}
\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).  These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).  The standard errors were calculated by considering the error propagation}
\begin{tabular}{l|l|l|l|l}
                & Active & SE   & Lazy &  SE \\ \hline
Clothing        & -481   & 26 & -45  & 9 \\ \hline
Footwear        & -264   & 23 & -49  & 8 \\ \hline
Appliances      & -242   & 29 & -20  & 2 \\ \hline
Photo-optics    & -410   & 30 & -39  & 3 \\ \hline
Homeware        & -127   & 18 & -14  & 1 \\ \hline
Household tools & -161   & 42 & -22  & 4 \\ \hline
Games           & -342   & 41 & -48  & 3
\label{Selling_sector_effects_TAB}
\end{tabular}
\end{center}
\end{table}

\begin{table}[]
\begin{center}
\caption{Redundancy funds variation (in terms of million of hours paid) for the scenarios where an active vs. lazy PM is considered. These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value). The standard errors were calculated by considering the error propagation.}
\begin{tabular}{l|l|l|l|l}
             & Active &  SE  & Lazy &   SE  \\ \hline
Total        & 2938   & 38 & 889  & 9.7 \\ \hline
Manufacture  & 2180   & 38 & 648  & 9.7 \\ \hline
Trade        & 52     & 3  & 19   & 0.8 \\ \hline
Construction & 407    & 11 & 135  & 2.8
\label{CIG_sector_effects_TAB}
\end{tabular}
\end{center}
\end{table}

>>>>

As a consequence, the lock-down efficacy,  within certain limits,  can be tuned.  In the literature, different scholars \cite{kabir2020evolutionary,rowthorn2020cost} challenged the issue of finding the optimal lock-down policy for minimizing the economic impact as well as the deaths.  In particular, for the model in Ref. \cite{kabir2020evolutionary}, it is assumed that the PM can impose a continuous factor for the lock-down (e.g., he/she can reduce the daily number of contacts between people by choosing each value between a definite range). In contrast, for different countries, such a factor seems to be much more discrete (e.g., the PM can reduce the daily contacts only by choosing definite values). Moreover it is assumed that the policy-maker perfectly knows the consequences of his/her choices and that he/she can act without delay to impose the optimal choice: this feature is entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy-maker.  Here we would propose here an alternative way to model the decision of the policy-maker that is based on a stochastic model instead of on a deterministic one. Moreover we will consider a discrete intensity for the lock-down. Finally,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on redundancy funds (\textit{Cassa Integrazione Ordinaria}) in Italy.  Thus, the final output of the model will be the cumulative deaths, the economic damage for each sales sector and the the increase of redundancy funds paid.
Here we will also consider that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them should assisted by the national health system.  As we will show by varying with continuity the probabilistic parameter by which the PM imposes the lock-down,  a discontinuity in the SIRD model and the lock-down days was obtained.  Such behaviour belongs to a class of phenomena that, in physical sciences, is called a phase transition.  For each phase, we will discuss the result of the simulation, and then we will compare them to get a general insight.

@@

\begin{table}[]
\begin{center}
\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).  These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).  The standard errors were calculated by considering the error propagation}
\begin{tabular}{l|l|l|l|l}
                & Active & SE   & Lazy &  SE \\ \hline
Clothing        & -481   & 26 & -45  & 9 \\ \hline
Footwear        & -468   & 23 & -49  & 8 \\ \hline
Appliances      & -242   & 29 & -20  & 2 \\ \hline
Photo-optics    & -410   & 30 & -39  & 3 \\ \hline
Homeware        & -127   & 18 & -14  & 1 \\ \hline
Household tools & -161   & 42 & -23  & 4 \\ \hline
Games           & -342   & 41 & -48  & 3
\label{Selling_sector_effects_TAB}
\end{tabular}
\end{center}
\end{table}

\begin{table}[]
\begin{center}
\caption{Redundancy funds variation (in terms of million of hours paid) for the scenarios where an active vs. lazy PM is considered. These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value). The standard errors were calculated by considering the error propagation.}
\begin{tabular}{l|l|l|l|l}
             & Active &  SE  & Lazy &   SE  \\ \hline
Total        & 2938   & 48 & 889  & 12.5 \\ \hline
Manufacture  & 2180   & 43 & 648  & 11 \\ \hline
Trade        & 52     & 3  & 19   & 0.6 \\ \hline
Construction & 407    & 6.8 & 135  & 1.7
\label{CIG_sector_effects_TAB}
\end{tabular}
\end{center}
\end{table}
